% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{ALFIN WILLIAM}

\basicInfo{
  \email{alfinwilliam@gmail.com} \textperiodcentered\ 
  \phone{(+91) 812-941-4204} \textperiodcentered\ 
  \linkedin[alfinwilliam]{https://www.linkedin.com/in/alfin-william-91b20832/}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Kerala Technological University (KTU)}, Trivandrum, Kerala}{2018 -- Present}
\textit{Master student} in Computer Applications (MCA), expected June 2020
\datedsubsection{\textbf{Kerala University}, Trivandrum, Kerala}{2014 -- 2017}
\textit{B.Sc} in Computer Science (CS)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{White Oval Technologies} Trivandrum, Kerala}{May 2017 -- Nov 2017}
\role{ASP.NET Developer Intern}{Manager: Aswin Blix TC}
Brief introduction: Developed and maintained ASP.NET Web applications
\begin{itemize}
  \item Implemented Employee Management System
  \item Optimized Employee efficiency
  \item Developed integrated employee environment.
\end{itemize}

\datedsubsection{\textbf{ Projects}}{Jan. 2016 -- May 2016}
\role{Student Spot}{Collaborated with Team members}
Brief introduction: Automation of University result to student app.
\begin{itemize}
  \item Implemented personalized result feature
  \item Optimized result delivery format
  \item created custom notification
\end{itemize}

\datedsubsection{\textbf{E-doctor}}{Jan. 2017 -- May 2017}
\role{Patient-Aid android app}{Collaborated with Team members}
Brief introduction: Virtual consulation , patient record storage.
\begin{itemize}
  \item Notification of medicine timings.
  \item Virtual consultation with specialist.
  \item Patient record storage.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Python, C++, HTML, CSS 
  \item Platform: Linux, Windows
  \item Tools: Git, Docker, Photoshop, Premiere Pro, MS Office
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1} Prize}, Group Discussion Winner on Dristi 2017 by College Of Engineering TVM }{Mar. 2017}
\datedline{\textit{\nth{1} Prize}, Best Management Team on Pheonix 2017 by Marthoma College of Engineering TVM }{Mar. 2017}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Interests: Hobby Cyclist, Youtube Motovlogger, Photographer, Cinephile, bibliophile
  \item Website: http://alfinwilliam.me
  \item GitHub: https://github.com/alfinwilliam
  \item Languages: English, French, Hindi, Tamil, Malayalam - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
